\myTitle

### 2024-03-15 002-GSI_and_Fst.Rmd
Update for new pops.  Also revamp FST fig.
(to have scatter plots in lower diagonals.)

# and now do some formatting
fbmet5 <- fbmet4 %>%
  ungroup() %>%
  mutate(
    `Sampling Months` = sprintf("\\raisebox{-0.12 em}{\\includegraphics[height=1.02em]{../%s}}", sparkline_path),
    `Year Range` = sprintf("%d--%d", min_year, max_year)
  ) %>%
  select(`Mainstem River`, abbrv, map_text, run_timing_for_table, ESU, N, N_date, `Sampling Months`, `Year Range`) %>%
  mutate(map_text = str_replace(map_text, ",.*$", "")) %>% # this removes the abbreviations after the commas on the map names
  mutate(N_date = replace_na(N_date, 0L)) %>%
  rename(
    `Mainstem River$^1$` = `Mainstem River`,
    Code = abbrv,
    `Location Name$^2$` = map_text,
    Run = run_timing_for_table,
    `ESU$^3$` = ESU,
    `$N$` = N,
    `$N_\\mathrm{day}$` = N_date
  ) %>%
  arrange(factor(Code, levels = collection_order))

@@

@@

In order to do this we need to convert the data to a lumped format.
This means making integers of the alleles and then catenating them.
One locus has 11 allele, so we should use two digits for each allele.  We drop the
LFAR from this, because those were chosen specifically to be weird in the late fall.
```{r, cache=TRUE}
full_base_long <- full_base2 %>% 
  select(-starts_with("NC_037130.1")) %>%  # drop the LFARs
  mutate(
    Pop = as.integer(factor(collection, levels = collection_order)),
    .before = collection
  ) %>%
  select(-repunit, -collection, -sample_type) %>%
  pivot_longer(
    cols = c(-indiv, -Pop),
    names_to = c("locus", "gene_copy"),
    names_pattern = "^(.*)_([12])$"
  )

@@

# Adding genic differentiation values to lower triangle and making a figure

We are going to use genepop to compute p-values for differentiation.  To do
that we need to make a genepop file.
```{r}
gpt <- full_base2 %>%
  select(-repunit, -sample_type) %>%
  pivot_longer(
    cols = -c(indiv, collection),
    names_to = c("locus", "gene_copy"),
    values_to = "allele",
    names_pattern = "(.*)[_.]([12])$"
  ) %>%
  group_by(locus) %>%
  mutate(alle_int = replace_na(as.integer(factor(allele)), 0L)) %>%
  ungroup() %>%
  mutate(alle_str = sprintf("%02d", alle_int)) %>%
  select(-allele, -alle_int) %>%
  pivot_wider(
    names_from = gene_copy,
    values_from = alle_str
  ) %>%
  mutate(geno = str_c(`1`, `2`)) %>%
  select(-`1`, -`2`) %>%
  pivot_wider(
    names_from = locus,
    values_from = geno
  ) %>%
  select(-indiv)

gpt_nest = gpt %>%
  mutate(collection2 = str_c(collection, ","), .after = collection) %>%
  group_by(collection) %>%
  nest()

# now we write that out to a file
outf <- "results/GSI_and_Fst/genepop.txt"
cat("Baseline data set in genepop format\n    ", file = outf)
cat(names(gpt)[-1], sep = ",", file = outf, append = TRUE)
cat("\n", file = outf, append = TRUE)
for(x in gpt_nest$data) {
    cat("POP\n", file = outf, append = TRUE); 
    write_tsv(x, col_names = FALSE, file = outf, append = TRUE)
  }
```

Now, we could use the genepop package to get results from that file, but it
is crazy slow, so we do not do this.
```r
td_file <- "results/GSI_and_Fst/genic_tests.txt"
genepop::test_diff(inputFile = outf, pairs = TRUE, outputFile = td_file)
```

OK! HERE IS WHAT WE WILL DO: MAKE THIS PARALLELIZABLE.  WE WILL MODIFY THE ABOVE
TO MAKE A GENEPOP FILE FOR EVERY LOCUS, AND THEN WE WILL JUST RUN OVER ALL THOSE
LOCI USING mclappy ON 8 CORES ON MY LAPTOP, TO MAKE IT FASTER.  THEN, WE WILL PRESENT
THE RESULTS AS A TINY-MULTIPLE HISTOGRAM OF THE P-VALUES IN EACH CELL.  KINDA COOL!

@@

# once again, make it looks like rubias output and taf_prep() it.
lower_tri_diag <- wgs_mat %>%
  mutate(
    collection_f = factor(pop1_f, levels = collection_order),
    inferred_coll_f = factor(pop2_f, levels = collection_order),
    n = fst
  ) %>%
  select(collection_f, inferred_coll_f, n) %>%
  complete(collection_f, inferred_coll_f) %>%
  filter(as.integer(collection_f) >= as.integer(inferred_coll_f)) %>%  # this gets lower tri + diagonal
  taf_prep()

# then we put those together and make a figure
full_fst <- bind_rows(
  upper_tri_fst,
  lower_tri_diag
) %>%
  arrange(row_label, col_label)

# get the result
TAF_FST <- table_as_figure(
  X = full_fst, 
  RC_groups = RC_groups,
  external_colors = run_time_colors,
  internal_colors = repunit_colors,
  Xs_on_diagonal = TRUE,
  plot_margins = c(0.7, 0.1, 0.1, 0.1)
)

# and plot it
TAF_FST$full_plot

@@

And we can save that too:
```{r}
ggsave(TAF_FST$full_plot, file = output_list$fst_table, width = 6, height = 5.1)
```

@@

```{r}
gsi_fst_fig_for_paper <- plot_grid(
  TAF2$full_plot,
  plot_grid(
    get_legend(TAF2$for_external_legend),
    get_legend(TAF2$for_internal_legend),
    nrow = 1
  ),
  TAF_FST$full_plot,
  nrow = 3,
  rel_heights = c(6,1.5,6)
)

>>>>

# and now do some formatting
fbmet5 <- fbmet4 %>%
  ungroup() %>%
  mutate(
    `Sampling Months` = sprintf("\\raisebox{-0.12 em}{\\includegraphics[height=1.02em]{../%s}}", sparkline_path),
    `Year Range` = sprintf("%d--%d", min_year, max_year)
  ) %>%
  select(`Mainstem River`, abbrv, map_text, run_timing_for_table, ESU, N, N_date, `Sampling Months`, `Year Range`) %>%
  mutate(map_text = str_replace(map_text, ",.*$", "")) %>% # this removes the abbreviations after the commas on the map names
  mutate(N_date = replace_na(N_date, 0L)) %>%
  rename(
    `Mainstem River$^1$` = `Mainstem River`,
    Code = abbrv,
    `Location Name$^2$` = map_text,
    Run = run_timing_for_table,
    `ESU$^3$` = ESU,
    `$N$` = N,
    `$N_\\mathrm{day}^4$` = N_date
  ) %>%
  arrange(factor(Code, levels = collection_order))

@@

Rubias_for_later <- X2 # keeping this for later...

@@

In order to do this we need to convert the data to a lumped format.
This means making integers of the alleles and then catenating them.
One locus has 11 allele, so we should use two digits for each allele.  We drop the
LFAR from this, because those were chosen specifically to be weird in the late fall.
```{r}
full_base_long <- full_base2 %>% 
  select(-starts_with("NC_037130.1")) %>%  # drop the LFARs
  mutate(
    Pop = as.integer(factor(collection, levels = collection_order)),
    .before = collection
  ) %>%
  select(-repunit, -collection, -sample_type) %>%
  pivot_longer(
    cols = c(-indiv, -Pop),
    names_to = c("locus", "gene_copy"),
    names_pattern = "^(.*)_([12])$"
  )

@@

# Adding allele frequency scatter plots to the lower diagonal

I thought about doing differentiation tests, or histograms of per-locus
Fst values, but then I realized that it actually might be way more informative
to put small-multiple scatter plots of allele frequencies in each of the lower-diagonal
cells of the Fst figure.  I think it might look cool.

We will also standardize each sample size (at each locus) to the minimum
number of observed genotypes in a population.

## Calculate allele frequencies for each population and standardize to lowest sample size

Straightforward tidyverse stuff:
```{r}

# long format with no missing data
long_genos <- full_base2 %>%
  select(-repunit, -sample_type) %>%
  pivot_longer(
    cols = -c(indiv, collection),
    names_to = c("locus", "gene_copy"),
    values_to = "allele",
    names_pattern = "(.*)[_.]([12])$"
  ) %>%
  filter(!is.na(allele))

# now get the minimum sample sizes for each
min_sampled <- long_genos %>%
  count(collection, locus) %>%
  group_by(locus) %>%
  summarise(min_ngc = min(n))

# having looked at those, if we keep anything with
# at least 38 gene copies, we have most of the loci.
# So, we will use this to slice sample some individuals from
# each population. We have to do a bunch of rigamoral because
# slice_sample requires that the n argument is a constant.  BOGUS!
set.seed(5)
long_genos_subsampled <- long_genos %>%
  left_join(min_sampled, by = "locus") %>%
  filter(min_ngc >= 38) %>%
  group_by(collection, locus, min_ngc) %>%
  nest() %>%
  mutate(
    ssd = map2(.x = data, .y = min_ngc, .f = function(x, y) slice_sample(x, n = y))
  ) %>%
  select(-data) %>%
  unnest(ssd) %>%
  select(-min_ngc)

# get allele frequencies
alle_freqs <- long_genos_subsampled %>%
  count(collection, locus, allele) %>%
  group_by(collection, locus) %>%
  mutate(freq = n / sum(n)) %>%
  select(-n) %>%
  ungroup()

# get all pairwise comparisons of population allele frequencies
backbone <- expand_grid(
  row_coll =  unique(alle_freqs$collection),
  col_coll = unique(alle_freqs$collection),
  alle_freqs %>% distinct(locus, allele)
)

# now get the freqs on there, order the collections and ensure
# that we are on the diagonal and the lower triangle, and then also get
# the positions for each of the points.  We will allow that the whole
# scatterplot can be inset into the cell by a fractional amount inset
inset <- 0.15
pair_freqs <- backbone %>%
  left_join(alle_freqs, by = join_by(row_coll == collection, locus, allele)) %>%
  rename(row_freq = freq) %>%
  left_join(alle_freqs, by = join_by(col_coll == collection, locus, allele)) %>%
  rename(col_freq = freq) %>%
  mutate(
    row_coll = factor(row_coll, levels = collection_order),
    col_coll = factor(col_coll, levels = collection_order)
  ) %>%
  filter(as.integer(col_coll) <= as.integer(row_coll)) %>%
  replace_na(list(row_freq = 0.0, col_freq = 0.0)) %>%
  mutate( # this is just setting things as in table_as_figure
      ymin = nlevels(row_coll) - as.integer(row_coll) + inset,
      ymax = nlevels(row_coll) - as.integer(row_coll) + 1 - inset,
      xmin = as.integer(col_coll) - 1 + inset,
      xmax = as.integer(col_coll) - inset
    ) %>%
  mutate(  # here we get the x-y positions for the scatter points
    x = xmin + col_freq * (xmax - xmin),
    y = ymin + row_freq * (ymax - ymin)
  )

@@

# we need to get colors and things for the fill.  We just take the
# rubias output that was run through taf_prep and we keep the lower
# diagonal and we set all the cell_labels to NA.
lower_tri_base <- Rubias_for_later %>%
  filter(as.integer(col_label) <= as.integer(row_label)) %>%
  mutate(cell_label = NA_character_)

# then we put those together and make a figure
full_fst <- bind_rows(
  upper_tri_fst,
  lower_tri_base
) %>%
  arrange(row_label, col_label)

# get the result
TAF_FST <- table_as_figure(
  X = full_fst, 
  RC_groups = RC_groups,
  external_colors = run_time_colors,
  internal_colors = repunit_colors,
  Xs_on_diagonal = FALSE,
  plot_margins = c(0.7, 0.1, 0.1, 0.1)
)

# then plot it and add the scatter points on the lower diagonal
fst_with_scatters <- TAF_FST$full_plot +
  geom_point(
    data = pair_freqs,
    mapping = aes(x = x, y = y),
    size = 0.025,
    colour = "black"
  )

@@

And we can save that too:
```{r}
ggsave(fst_with_scatters, file = output_list$fst_table, width = 6, height = 5.1)
```

@@

```{r}
gsi_fst_fig_for_paper <- plot_grid(
  TAF2$full_plot,
  plot_grid(
    get_legend(TAF2$for_external_legend),
    get_legend(TAF2$for_internal_legend),
    nrow = 1
  ),
  fst_with_scatters,
  nrow = 3,
  rel_heights = c(6,1.5,6)
)

### 2024-03-15 tex/body-text-of-paper.tex
Update for new pops.  Also revamp FST fig.
(to have scatter plots in lower diagonals.)

We sampled fish for the reference baselines from XX locations across California.
These locations included sites in the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley, the Klamath-Trinity basin in Northern California, and
3 rivers of the California coast (Russian, Eel, etc)
(Fig.~\ref{fig:map}).
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. Abbreviations used in location names as folows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%
Collections in each location were separated into fish from the different run-timing ecotypes according
to a variety of criteria. The last vestiges of winter-run Chinook salmon are maintained at the Livingston
Stone National Fish Hatchery for supplementation (released as juveniles into the river) and as a captive broodstock;
sampling of this population was performed by hatchery staff during spawning. In Central Valley Rivers with both 
spring and fall ecotypes (i.e. Mill, Deer and Butte Creeks), previous research has documented distinct/disparate/unique
spawning times (Julian date) for each ecotype (REF?). As such, sampling targeted carcasses found in each of these 
rivers at times representative of their run-timing designation, which we were able to further verify using their genotypes
at the RoSA markers. At the time of sampling, only fall-run Chinook were found in the San Joaquin River. Run-timing 
designation at the Feather River Hatchery is more complicated but is managed at a fine-scale by hatchery practices, 
where early returning fish in May and April (expressing the Spring-run life history) are visibly tagged and re-released 
to the river. Subsequently in the Fall, when hatchery raceways are reopened, only fish with the visible tag are included
as Spring-run broodstock. Individual-based analyses of RoSA genotypes have demonstrated

(We need to talk about how these were split into spring run, fall-run, winter 
run, etc.
In total, the samples in the baseline represent fish from five different Evolutionarily Significant 
Units (ESUs) of Chinook salmon \citep{waples1991pacific} A summary of the different collections 
%%%%%%%%%%%%%%%%
\begin{table*}
\caption{\footnotesize Collections of fish in the reference baseline.  The Sampling Months column shows
a pictorial representation of the proportion of each collection sampled in each month.  Colors in
this column correspond to run-timing groups as described in the caption of Fig.~\protect\ref{fig:map}.}
{\small 
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} lllllrcr}
\hline\hline\vspace*{0.4ex}
\input{inputs/samples-table.tex}
\end{tabular*}
}
\rule{3cm}{0.3pt}

{\footnotesize
$^1$R. = River.\\
$^2$Ck. = Creek; NFH = National Fish Hatchery; R. = River; H. = Hatchery.\\
$^3$ESU = Evolutionarily Significant Unit; CVFR = Central Valley Fall Run ESU; CVSR = Central Valley Spring Run ESU; CVWR = 
Central Valley Winter Run ESU; CC = California Coastal ESU; UKTR = Upper Klamath and Trinity Rivers ESU.
}
\hrule\vspace*{0.3ex}\hrule
\end{table*}
%%%%%%%%%%%%%%%%%%%%%

@@

After designing and validating an amplicon-sequencing approach to type both the
existing SNPtype assays and the product of the additional microhaplotype
discovery process we identified their location with the genome. We mapped the reference
sequences for these markers 
to the Chinook v2.0 genome assembly \citep{christensen2018chinook}
with both the Burrows-Wheeler Aligner \citep{bwa-mem2009} and the BLAST-like Alignment tool \citep{kent2002blat}.
We report the genomic coordinates these target amplicons found with both alignment methods.

@@

\begin{figure}
\newcommand{\examplecap}{\footnotesize Self-assignment rates  ({\bf a)} and pairwise 
$F_\mathrm{ST}$ values ({\bf b)} for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  For self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection. For $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data and the lower triangle was calculated with the whole genome sequence data (where available) 
from \citet{thompson2020complex}.  NOTE: I THINK WE SHOULD MAKE THE LOWER 
DIAGONAL THE P-VALUE FROM A TEST OF DIFFERENTIATION OR SOMETHING LIKE THAT.}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\examplecap]{\examplecap}
\label{fig:example}
\end{figure}

>>>>

We sampled fish for the reference baselines from XX locations across California.
These locations included sites in the two
main tributaries (the Sacramento River and the San Joaquin River) within
California's Central Valley, the Klamath-Trinity basin in Northern California, and
3 rivers of the California coast (Russian, Eel, etc)
(Fig.~\ref{fig:map}).
%%%%%%%%%%%%%
\begin{figure}
\newcommand{\mapcap}{\footnotesize  A map of sampling locations represented in the reference 
baseline.  The colored circles aside
each location name represent the different run-timing groups of Chinook salmon
included in the collections from the location.  Color codes are as follows: \Wball~=~Winter run,
\LFball{}~=~Late-fall run, \Fball~=~Fall run, \Sball~=~Spring run. 
Names of each location are followed by the codes used to refer to fish from each location, with
{\tt XXF/S} indicating {\tt XXF} and {\tt XXS} are used to denote fall-run and spring-run fish
from location {\tt XX}.  Abbreviations used in location names as follows: R. = River; Ck. = Creek; H. = Hatchery; NFH = National Fish Hatchery.}
\begin{center}
\includegraphics[width=\columnwidth]{images/map-crop.pdf}
\end{center}
\caption[\mapcap]{\mapcap}
\label{fig:map}
\end{figure}
%%%%%%%%%%%%%%%
Collections in each location were separated into fish from the different run-timing ecotypes according
to a variety of criteria. The last vestiges of winter-run Chinook salmon are maintained at the Livingston
Stone National Fish Hatchery for supplementation (released as juveniles into the river) and as a captive broodstock;
sampling of this population was performed by hatchery staff during spawning. In Central Valley Rivers with both 
spring and fall ecotypes (i.e. Mill, Deer and Butte Creeks), previous research has documented distinct/disparate/unique
spawning times (Julian date) for each ecotype (REF?). As such, sampling targeted carcasses found in each of these 
rivers at times representative of their run-timing designation, which we were able to further verify using their genotypes
at the RoSA markers. At the time of sampling, only fall-run Chinook were found in the San Joaquin River. Run-timing 
designation at the Feather River Hatchery is more complicated but is managed at a fine-scale by hatchery practices, 
where early returning fish in May and April (expressing the Spring-run life history) are visibly tagged and re-released 
to the river. Subsequently in the Fall, when hatchery raceways are reopened, only fish with the visible tag are included
as Spring-run broodstock. Individual-based analyses of RoSA genotypes have demonstrated

(We need to talk about how these were split into spring run, fall-run, winter 
run, etc.
In total, the samples in the baseline represent fish from five different Evolutionarily Significant 
Units (ESUs) of Chinook salmon \citep{waples1991pacific} A summary of the different collections 
%%%%%%%%%%%%%%%%
\begin{table*}
\caption{\footnotesize Collections of fish in the reference baseline.  The Sampling Months column shows
a pictorial representation of the proportion of each collection sampled in each month.  Colors in
this column correspond to run-timing groups as described in the caption of Fig.~\protect\ref{fig:map}.}
{\small 
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} llllllrcr}
\hline\hline\vspace*{0.4ex}
\input{inputs/samples-table.tex}
\end{tabular*}
}
\rule{3cm}{0.3pt}

{\footnotesize
$^1$R. = River.\\
$^2$Ck. = Creek; NFH = National Fish Hatchery; R. = River; H. = Hatchery.\\
$^3$ESU = Evolutionarily Significant Unit; CVFR = Central Valley Fall Run ESU; CVSR = Central Valley Spring Run ESU; CVWR = 
Central Valley Winter Run ESU; CC = California Coastal ESU; UKTR = Upper Klamath and Trinity Rivers ESU. \\
$^4N_\mathrm{day}$: the number of samples for which the specific sampling day was recorded.
}
\hrule\vspace*{0.3ex}\hrule
\end{table*}
%%%%%%%%%%%%%%%%%%%%%

@@

After designing and validating an amplicon-sequencing approach to type both the
existing SNPtype assays and the product of the additional microhaplotype
discovery process we identified their location with the genome. We mapped the reference
sequences for these markers 
to the Chinook v2.0 genome assembly (\url{https://www.ncbi.nlm.nih.gov/datasets/genome/GCF_018296145.1/})
with both the Burrows-Wheeler Aligner \citep{bwa-mem2009} and the BLAST-like Alignment tool \citep{kent2002blat}.
We report the genomic coordinates these target amplicons found with both alignment methods.

@@

\begin{figure}
\newcommand{\examplecap}{\footnotesize Self-assignment rates  ({\bf a)} and pairwise 
$F_\mathrm{ST}$ values and allele frequencies ({\bf b)} for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  For self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection. In ({\bf b}), for $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data. Each cell in the lower triangle shows a small scatter plot of estimated allele frequencies
in the collections.  These frequencies were estimated by, for each locus, randomly
subsampling individuals from each collection to the minimum number of observed alleles in any collection
at the locus.  }
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\examplecap]{\examplecap}
\label{fig:example}
\end{figure}

### 2024-03-15 tex/inputs/samples-table.tex
Update for new pops.  Also revamp FST fig.
(to have scatter plots in lower diagonals.)

Mainstem River$^1$&Code&Location Name$^2$&Run&ESU$^3$&$N$&Sampling Months&Year Range\tabularnewline
\hline Sacramento R.&BCF&Butte Ck.&Fall&CVFR&45&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-BCF_Butte-Creek.pdf}}&2004--2016\tabularnewline
Sacramento R.&BCS&Butte Ck.&Spring&CVSR&116&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-BCS_Butte-Creek.pdf}}&2004--2017\tabularnewline
Sacramento R.&CHLF&Coleman NFH&Late-fall&CVFR&261&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-CHLF_Coleman-National-Fish-Hatchery.pdf}}&2011--2015\tabularnewline
Sacramento R.&MDF&Deer Ck.&Fall&CVFR&29&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDF_Deer-Creek.pdf}}&2002--2004\tabularnewline
Sacramento R.&MDS&Deer Ck.&Spring&CVSR&34&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDS_Deer-Creek.pdf}}&2002--2002\tabularnewline
Sacramento R.&FRHF&Feather R. H.&Fall&CVFR&106&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-FRHF_Feather-River-Hatchery.pdf}}&2008--2010\tabularnewline
Sacramento R.&FRHS&Feather R. H.&Spring&CVSR&202&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-FRHS_Feather-River-Hatchery.pdf}}&2010--2019\tabularnewline
Sacramento R.&MDF&Mill Ck.&Fall&CVFR&53&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDF_Mill-Creek.pdf}}&2002--2004\tabularnewline
Sacramento R.&MDS&Mill Ck.&Spring&CVSR&51&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDS_Mill-Creek.pdf}}&2002--2004\tabularnewline
Russian R.&RRF&Warm Springs H.&Fall&CC&92&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-RRF_Warm-Springs-Hatchery.pdf}}&2012--2012\tabularnewline
Sacramento R.&SRW&Livingston Stone NFH&Winter&CVWR&111&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-SRW_Livingston-Stone-National-Fish-Hatchery.pdf}}&2013--2014\tabularnewline
San Joaquin R.&SJRF&San Joaquin R.&Fall&CVFR&79&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-SJRF_San-Joaquin-River.pdf}}&2016--2016\tabularnewline
Trinity R.&TRF&Trinity R. H.&Fall&UKTR&41&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-TRF_Trinity-River-Hatchery.pdf}}&2012--2012\tabularnewline
Trinity R.&TRS&Trinity R. H.&Spring&UKTR&46&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-TRS_Trinity-River-Hatchery.pdf}}&2012--2012\tabularnewline

>>>>

Mainstem River$^1$&Code&Location Name$^2$&Run&ESU$^3$&$N$&$N_\mathrm{day}^4$&Sampling Months&Year Range\tabularnewline
\hline Rogue R.&CRHS&Cole Rivers H.&Spring&SONCC&50&0&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-CRHS_Cole-Rivers-Hatchery.pdf}}&2004--2010\tabularnewline
Smith R.&SmRF&Smith R.&Fall&SONCC&46&46&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-SmRF_Smith-River.pdf}}&2010--2011\tabularnewline
Klamath R.&BCkF&Blue Ck.&Fall&SONCC&56&56&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-BCkF_Blue-Creek.pdf}}&2008--2008\tabularnewline
Klamath R.&IGHF&Iron Gate H.&Fall&UKTR&93&92&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-IGHF_Iron-Gate-Hatchery.pdf}}&2017--2017\tabularnewline
Trinity R.&TRS&Trinity R. H.&Spring&UKTR&46&46&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-TRS_Trinity-River-Hatchery.pdf}}&2012--2012\tabularnewline
Trinity R.&TRF&Trinity R. H.&Fall&UKTR&41&41&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-TRF_Trinity-River-Hatchery.pdf}}&2012--2012\tabularnewline
Eel R.&ERF&Eel R.&Fall&CCC&93&0&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-ERF_Van-Arsdale-Fisheries-Station.pdf}}&2014--2014\tabularnewline
Russian R.&RRF&Warm Springs H.&Fall&CCC&92&92&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-RRF_Warm-Springs-Hatchery.pdf}}&2012--2012\tabularnewline
Sacramento R.&SRW&Livingston Stone NFH&Winter&CVWR&109&19&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-SRW_Livingston-Stone-National-Fish-Hatchery.pdf}}&2013--2014\tabularnewline
Sacramento R.&BCS&Butte Ck.&Spring&CVSR&114&114&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-BCS_Butte-Creek.pdf}}&2004--2017\tabularnewline
Sacramento R.&MDS&Deer Ck.&Spring&CVSR&32&32&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDS_Deer-Creek.pdf}}&2002--2002\tabularnewline
Sacramento R.&MDS&Mill Ck.&Spring&CVSR&49&49&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDS_Mill-Creek.pdf}}&2002--2004\tabularnewline
Sacramento R.&FRHS&Feather R. H.&Spring&CVSR&202&202&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-FRHS_Feather-River-Hatchery.pdf}}&2010--2019\tabularnewline
Sacramento R.&FRHF&Feather R. H.&Fall&CVFR&106&106&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-FRHF_Feather-River-Hatchery.pdf}}&2008--2010\tabularnewline
Sacramento R.&BCF&Butte Ck.&Fall&CVFR&44&44&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-BCF_Butte-Creek.pdf}}&2004--2016\tabularnewline
Sacramento R.&MDF&Deer Ck.&Fall&CVFR&22&22&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDF_Deer-Creek.pdf}}&2002--2004\tabularnewline
Sacramento R.&MDF&Mill Ck.&Fall&CVFR&48&48&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-MDF_Mill-Creek.pdf}}&2002--2004\tabularnewline
San Joaquin R.&SJRF&San Joaquin R.&Fall&CVFR&79&79&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-SJRF_San-Joaquin-River.pdf}}&2016--2016\tabularnewline
Sacramento R.&CHLF&Coleman NFH&Late-fall&CVFR&252&252&\raisebox{-0.12 em}{\includegraphics[height=1.02em]{../tex/images/months-CHLF_Coleman-National-Fish-Hatchery.pdf}}&2011--2015\tabularnewline
